SMT-COMP 2023\\ 18th International Satisfiability Modulo Theory Competition

### 2023-07-05 2023/slides/presresults/slides.tex
Start of presentation result 2023

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2022 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2022\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 11, 2022}

%% Institut
\institute{
  Universidade Federal de Minas Gerais, Brazil \and
  Albert-Ludwigs-Universit\"at Freiburg, Germany \and
  CEA List, France
}

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        391\,363 instances {\small (+9680)}\\
        with 1 query each \\
        in 81 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,285 instances {\small (+1)}\\
        with 33\,998\,935 queries {\small (+141)} \\
        in 39 logics.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
  \pause
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Non-incremental}
        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
          instances\\
          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
        }
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Incremental}
        22\,300 instances
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}

@@

\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
  Teams: 21 (+3)
  \bigskip

  \begin{tabular}{c|r@{}l|r@{}l|c}
    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
    \hline
    Single Query  &  22&(+3)  & 19&(+1)  & 93\,945 \\
    Incremental &  8&(+1)   & 17&(+2)  & 22\,300   \\
    Unsat Core  &  6&(-1)   & 18&(+1)  & 57\,245  \\
    Model Validation  &  8&(+1)    &  7& (+ 1 exp.)  & 32\,766  \\
    Proof Exhibition  &  &4    &  & 18 exp.  & 57\,245  \\
    \hline
    Parallel &   4&(+1)      &   &14 exp.  & 400 \\
    Cloud & 4&(-1)      &  &14 exp.  & 400 \\

@@

  Number in parenthesis shows changes from 2021
\end{frame}

@@

  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
  \begin{itemize}
  \item CDCL(T)
  \item mcSAT
  \item saturation
  \item automata
  \item finite domain
  \item CP
  \item local search
  \item besides wrappers extending the scope of existing solvers
  \end{itemize}

  \bigskip
  Six new solvers participated:
  \begin{itemize}
  \item NRA-LS   {\footnotesize (Liu et al.)}
  \item OSTRICH {\footnotesize (Chen et al.)}
  \item Yices-ismt {\footnotesize (Jia et al.)}
  \item Z3++ {\footnotesize (Cai et al.)}
  \item solsmt {\footnotesize (Reitwiessner and Soos)}
  \end{itemize}

@@

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-ostrich.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtrat.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-stp.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-verit.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
\end{frame}
}

{
  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
      \item Q3B
      \vitem SMT-RAT
      \vitem SMTS
      \vitem UltimateEliminatior+MathSAT
      \vitem Vampire
      \vitem Z3str4
    \end{itemize}
  \end{frame}
}

@@

\begin{frame}{Division Winners}
  \pause
  \emph{Single Query, sequential score}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}

  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}

  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}

  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}

  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
  \end{itemize}

  \medskip

  \pause
  \emph{Unsat Core}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
\item \emph{Vampire}: Equality(Par)
\item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
\item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
\item \emph{UltimateEliminator+MathSAT}: FPArith

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
\item \emph{Bitwuzla}: FPArith, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith
  \end{itemize}
  \medskip

  \pause
  \emph{Model Validation (competitive only)}
  \begin{itemize}
\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
\item \emph{smtinterpol}: QF\_Equality+LinearArith
\item \emph{Yices2}: QF\_Equality
\item \emph{Z3++}: QF\_LinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith

\item experimental: QF\_FPArith : Bitwuzla, cvc5

  \end{itemize}
\end{frame}

\begin{frame}{Largest contribution}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
    \pause

    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+LA)} &
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\

    par &  cvc5&{\tiny(Eq+NA)}&
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
\\[3pt]
    \pause
    \emph{Model Validation}\\
    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
  \end{tabular}
\end{frame}

\begin{frame}{Biggest Lead}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & SMTInterpol&{\tiny(QF\_NIA)}
    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
    \pause
    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
    \pause
    \emph{Model Validation}\\
    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
  \end{tabular}
\end{frame}

@@

  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)

@@

  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
  yices-ismt
  \begin{itemize}
    \item Down from 10 last year
    \pause
    {\tiny (but note that this may be because of our issue with ignoring most of the
    new benchmarks in the selection)}

  \end{itemize}
  \end{itemize}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2023 - 
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2023\\
18th International Satisfiability Modulo Theory Competition}
\author{Martin Bromberger \and Jochen Hoenicke \and \emph{Fran\c{c}ois Bobot}}
\date{July 5, 2023}

%% Institut
\institute{
CEA List, France \and
MPI für Informatik, Germany \and
Certora, Israel
}

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        434\,212 instances {\small (+42849)}\\ % 434212-391363=42849
        with 1 query each \\
        in 83 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,287 instances {\small (+2)}\\
        with 34\,036\,491 queries {\small (+37\,556)} \\ %34036491-33998935=37556
        in 38 logics. % -1 ???
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
  \pause
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Non-incremental}
        227\,940 instances
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Incremental}
        22\,302 instances
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}

@@

\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
  Teams: 25 (+4) %2022 21
  \bigskip

  \begin{tabular}{c|r@{}l|r@{}l|c}
    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
    \hline
    Single Query  &  22&(=)  & 19&(=)  & 113\,139 \\
    Incremental &  7&(-1)   & 17&(=)  & 22\,301   \\
    Unsat Core  &  6&(=)   & 16&(-1)  & 72\,958  \\
    Model Validation  &  11&(+3)    &  13& (+ 6 exp.)  & 61\,083  \\
    Proof Exhibition  &  4&(=)    &  & 19 exp.  & 59\,114  \\
    \hline
    Parallel &   3&(-1)      &   &4 exp.  & 400 \\
    Cloud & 2&(-2)      &  &4 exp.  & 400 \\

@@

  Number in parenthesis shows changes from 2022
\end{frame}

@@

  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
  \begin{itemize}
  \item CDCL(T), Saturation, MCSAT, CP
  \item automata
  \item finite domain
  \item local search
  \item besides wrappers extending the scope of existing solvers
  \end{itemize}

  \bigskip
  Seven new solvers participated:
  \begin{itemize}
\item iProver {\footnotesize (Korovin et al.)}
\item SMT-RAT-MCSAT {\footnotesize (Jasper Nalbach et al.)}
\item UltimateIntBlastingWrapper+SMTInterpol {\footnotesize (Max Barth et al.)}
\item Yaga {\footnotesize (Hanák et al.)}
\item Z3-alpha {\footnotesize (Lu et al.)}
\item Z3-Noodler {\footnotesize (Havlena et al.)}
\item Z3-Owl {\footnotesize (Ma et al.)}
\end{itemize}

@@

\newcommand{\myincludepdf}[1]{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{#1}}
\end{frame}
}

  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
      \item Q3B
      \vitem SMT-RAT
      \vitem SMTS
      \vitem UltimateEliminatior+MathSAT
      \vitem Vampire
      \vitem Z3str4
    \end{itemize}
  \end{frame}

@@

{
  \newcommand{\seq}{\texttt{;}}
  \newcommand{\paral}{\textbardbl}
  \newcommand{\sat}{$\top$}
  \newcommand{\unsat}{$\bot$}
  \newcommand{\fast}{\texttt{24}}
  \newcommand{\inc}{inc}
  \newcommand{\uc}{uc}
  \newcommand{\mv}{mv}
  \newcommand{\cloud}{cloud}
  \newcommand{\paralTrack}{parallel}
  %\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
  \newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}

\def\newpage{}

\newcommand{\MakeOnePage}[6]{
    \begin{frame}
    \frametitle{#1}

    \medskip
    \ifstrempty{#2}{}{
    \textcolor{red!30!black!90}
    {\textit{Overall Winner}}

    \textcolor{black}{\large #2}

     \medskip
    }

    \ifstrempty{#3}{}{
    \textcolor{red!30!black!90} {\textit{Winner of the Division#5}}

     \textcolor{black}{\large#3}

     \medskip
    }

    \ifstrempty{#4}{}{
     \textcolor{red!30!black!90}  {\textit{Winner of the Logic#6
      \ifstrempty{#3}{}{(where it did not win the corresponding division)}}}

     \textcolor{black}{\large #4}
    }
    \vspace{2mm}
    \end{frame}
}

\input{input_for_certificates.tex}

}

% \begin{frame}{Division Winners}
%   \pause
%   \emph{Single Query, sequential score}
%   \begin{itemize}
%   \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}

%   \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
%     Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
%     Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}

%   \item \emph{OpenSMT}: {\small QF\_LinearIntArith}

%   \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}

%   \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
%   \end{itemize}

%   \medskip

%   \pause
%   \emph{Unsat Core}
%   \begin{itemize}
% \item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
% \item \emph{Vampire}: Equality(Par)
% \item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
% \item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
% \item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
% \item \emph{UltimateEliminator+MathSAT}: FPArith

%   \end{itemize}

% \end{frame}

% \begin{frame}{Division Winners}
%   \emph{Incremental}
%   \begin{itemize}
% \item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
% \item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
% \item \emph{Bitwuzla}: FPArith, QF\_FPArith
% \item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
% \item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
% \item \emph{OpenSMT}: QF\_LinearRealArith
%   \end{itemize}
%   \medskip

%   \pause
%   \emph{Model Validation (competitive only)}
%   \begin{itemize}
% \item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
% \item \emph{smtinterpol}: QF\_Equality+LinearArith
% \item \emph{Yices2}: QF\_Equality
% \item \emph{Z3++}: QF\_LinearIntArith
% \item \emph{OpenSMT}: QF\_LinearRealArith

% \item experimental: QF\_FPArith : Bitwuzla, cvc5

%   \end{itemize}
% \end{frame}

% \begin{frame}{Largest contribution}
%   \begin{tabular}{r|c@{}lc@{}lc@{}l}
%     &\textcolor{gold}{\textbf{1st Place}} &&
%     \textcolor{silver}{\textbf{2nd Place}} &&
%     \textcolor{bronze}{\textbf{3rd Place}}\\
%     \hline
%     \emph{Single Query}\\
%     seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
%     par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
%     sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
%     unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
%     24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
%     \pause
%     \emph{Incremental}\\
%     par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
%     &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
%     \pause

%     \emph{Unsat Core}\\
%     seq & cvc5&{\tiny(Eq+LA)} &
%     Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\

%     par &  cvc5&{\tiny(Eq+NA)}&
%     Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
% \\[3pt]
%     \pause
%     \emph{Model Validation}\\
%     seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
%         & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
%     par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
%         & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
%   \end{tabular}
% \end{frame}

% \begin{frame}{Biggest Lead}
%   \begin{tabular}{r|c@{}lc@{}lc@{}l}
%     &\textcolor{gold}{\textbf{1st Place}} &&
%     \textcolor{silver}{\textbf{2nd Place}} &&
%     \textcolor{bronze}{\textbf{3rd Place}}\\
%     \hline
%     \emph{Single Query}\\
%     seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
%     par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
%     sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
%     unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
%     24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
%     \pause
%     \emph{Incremental}\\
%     par & SMTInterpol&{\tiny(QF\_NIA)}
%     &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
%     \pause
%     \emph{Unsat Core}\\
%     seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
%     par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
%     \pause
%     \emph{Model Validation}\\
%     seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
%     par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
%   \end{tabular}
% \end{frame}

@@

  \vitem 300 benchmarks with disagreements (ABV,
  BV,
  LIA,
  NIA,
  QF\_ABV,
  QF\_AUFBV,
  QF\_BVFP,
  QF\_FP,
  QF\_NRA,
  QF\_SLIA,
  UF,
  UFDT,
  UFDTLIRA)

@@

  \vitem We had only ??? solvers with soundness issues: 
  \end{itemize}
\end{frame}
